cardinalR: Generating interesting high-dimensional data structures

### 2025-04-02 paper-cardinalR.Rmd
Added plan for example
Start writing on Swiss roll data

@@

>>>>

Research gap with `geozoo`, `snedata` packages...

@@

### Swiss Roll

To generalize the Swiss roll structure to arbitrary dimensions, we introduce a function `generate_swiss_roll(n, p, noise_sd)`, which constructs a high-dimensional version of the classic 3D Swiss roll while preserving its core characteristics.

The function generates `n` points in a `p`-dimensional space, where the first two dimensions (`X_1, X_2`) define the primary Swiss roll shape using a parametric equation:

$$
X_1 = t \cos(t), \quad X_2 = t \sin(t), \quad \text{where } t \sim U(0, 3\pi)
$$

The third dimension (`X_3`) introduces variation perpendicular to the roll, sampled uniformly from \([-1,1]\). Additional dimensions (`X_4` to `X_p`) extend the data structure by applying a **sinusoidal transformation** of the parameter `t`, ensuring continuity in higher-dimensional spaces:

$$
X_i = \frac{\sin(i t)}{i}, \quad \text{for } i \geq 4.
$$

This transformation ensures a gradual decay in variance across dimensions, mimicking real-world high-dimensional structures where later dimensions often capture subtler variations. Optionally, Gaussian noise (`\mathcal{N}(0, \sigma^2)`) can be added to all dimensions using `noise_sd` to simulate measurement variability.

# Examples

Add one or two datasets and evaluate how it will be useful.... (one with NLDR, one with clustering)
